### 2019-07-07 thesis-template/dummy.tex
update

\begin{figure}[!t]
\centering
  \begin{minipage}{0.3\textwidth}
  \centering
  \includegraphics[width=\textwidth]{img_new/brain_surf.PNG}
     \label{a)}
      a)
  \end{minipage}
  \begin{minipage}{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{img_new/brain_volume2.PNG}
    \label{b)}
    b)
  \end{minipage}
  \begin{minipage}{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{img_new/brain_cross-section.PNG}
    c)
    \label{b)}
  \end{minipage}
  \caption{\enquote{brain} test field: a) LTG($0^\circ$), b) LTG volume, c) cross-section}
\label{heart-ftle}
\end{figure}

\begin{figure}[!t]
\centering
  \begin{minipage}{0.3\textwidth}
  \centering
  \includegraphics[height=\textwidth]{img/inverse29.png}\label{1a}
    a)
    \label{a)}
  \end{minipage}
  \begin{minipage}{0.3\textwidth}
  \centering
    \includegraphics[height=\textwidth]{img/inverse51.PNG}\label{2a}
	b)
    \label{b)}
  \end{minipage}
  \begin{minipage}{0.3\textwidth}
  \centering
    \includegraphics[height=\textwidth]{img/inverse101.PNG}
	c)
    \label{b)}
  \end{minipage}
  \caption{ \protect a) some text 
  \protect b) some other text}
\label{res_ftle}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\begin{figure}[!t]
\centering
  \begin{minipage}[t]{0.4\textwidth}
   \centering
  \includegraphics[height=0.9\textwidth]{img_new/brain-TFL.png}
	a) TFLs: noise correction
    \label{a)}
  \end{minipage}
  \begin{minipage}[t]{0.4\textwidth}
   \centering
    \includegraphics[width=0.9\textwidth]{img/brain_ftle_surf_noisereduction.PNG}
	b) Hlawatsch's approach: noise correction
    \label{b)}
  \end{minipage}
\caption{\enquote{Brain} test field}
\label{brain_ftle_noise}
\end{figure}
\begin{figure}[!t]
\centering
  \begin{minipage}{0.3\textwidth}
  \centering
  \includegraphics[height=\textwidth]{img/inverse29.png}\label{1a}
    a)
    \label{a)}
  \end{minipage}
  \begin{minipage}{0.3\textwidth}
  \centering
    \includegraphics[height=\textwidth]{img/inverse51.PNG}\label{2a}
	b)
    \label{b)}
  \end{minipage}
  \begin{minipage}{0.3\textwidth}
  \centering
    \includegraphics[height=\textwidth]{img/inverse101.PNG}
	c)
    \label{b)}
  \end{minipage}
  \caption{ \protect a) some text 
  \protect b) some other text}
\label{res_ftle}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
